### 2019-12-05 manuscript/manuscript.rmd
matrix overlap figure now mostly legible

taxon_rectangles = lapply(
	sequence_matrices,
	function ( sequence_matrix ){
		clade_rects(sequence_matrix)
	}
) %>%
bind_rows()

@@

filtered_taxon_rectangles <- taxon_rectangles[!grepl("only", taxon_rectangles$matrix),]

ggplot(data=filtered_taxon_rectangles) +
	scale_x_continuous(name="x") +
	scale_y_continuous(name="y") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) +
	# scale_fill_manual(guide = guide_legend(reverse=TRUE))
	# scale_fill_manual(values = clade_colors, guide = guide_legend(reverse=TRUE))
	scale_fill_discrete(guide = guide_legend(reverse=TRUE)) +
	facet_wrap( ~ matrix )

@@

```{r matrix_overlap}

matrix_overlap_rectangles =
	lapply(sequence_matrices, function(x) lapply(sequence_matrices, function(y) overlap_rects(x,y))) %>%
	unlist(recursive=FALSE) %>%
	bind_rows()

ggplot(data=matrix_overlap_rectangles) +
	scale_x_continuous(name="x") +
	scale_y_continuous(name="y") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=MSA ), alpha=0.5) +
	facet_grid( matrix_1 ~ matrix_2 )

>>>>

no_subsets = unlist(lapply(sequence_matrices, function(x) !grepl("only|_D", x@matrix_name)))

taxon_rectangles = lapply(
	sequence_matrices[no_subsets],
	function ( sequence_matrix ){
		clade_rects(sequence_matrix)
	}
) %>%
bind_rows()

@@

ggplot(data=taxon_rectangles) +
	scale_x_continuous(name="x") +
	scale_y_continuous(name="y") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) +
	# scale_fill_manual(guide = guide_legend(reverse=TRUE))
	# scale_fill_manual(values = clade_colors, guide = guide_legend(reverse=TRUE))
	scale_fill_discrete(guide = guide_legend(reverse=TRUE)) +
	facet_wrap( ~ matrix )

@@

```{r matrix_overlap, fig.height = 12, fig.width = 20}

matrix_overlap_rectangles =
	lapply(sequence_matrices[no_subsets], function(x) lapply(sequence_matrices[no_subsets], function(y) overlap_rects(x,y))) %>%
	unlist(recursive=FALSE) %>%
	bind_rows()

ggplot(data=matrix_overlap_rectangles) +
	scale_x_continuous(name="Genes") +
	scale_y_continuous(name="Species") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=MSA ), alpha=0.5) +
	facet_grid( matrix_1 ~ matrix_2, scales="free" ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), strip.text.y = element_text(angle = 0), strip.text.x = element_text(angle = 60))
